Results

### 2021-08-16 Analysis/03_Summarise_results.Rmd
TODO

```{r, echo = FALSE}
## Extracting all the scaled results
scaled_results <- extract.table(all_results, scale.method = "between")
scaled_within <- extract.table(all_results, scale.method = "within")
```

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
fancy.plot(scaled_results, col = c("blue", "orange"))
```

Figure X1: Simulation results: the y axes represent the different metrics tested (sorted by categories). The different columns represent the different stressors. The x-axes represent the metric values centred on the random changes and scaled by the maximum value for each metric between the four stressors. Negative and positive values signify a decrease/increase in the metric score. The dots represent the median metric value, the full line their 50% confidence interval (CI) and the dashed line their 95% CI. The colours are just here to visually separate the metrics rows but the colour gradient within each row corresponds to a removal of respectively 80%, 60%, 40% and 20% of the data (from top to bottom).

@@

Figure X2: See above + Grey lines in the background are a fitted linear model on the scaled metric score function of removal amount and the value displayed is the adjusted R^2 from each of these models. Dashed grey lines represent non-significant models (slope or/and intercept). The grey line plots represent (CI + median) represent distribution of metrics scores not clearly different from the random metric scores (paired t-test p value > 0.05).

> I think that Figure X2 would do a good summary of how the metrics pick up changes. Here's a couple of interpretations of it in the light of my previous work on which metric to choose:
  * Don't use the TPD richness metric, it doesn't do much.
  * On the other hand, hypervolume regularity and richness are two good metrics because they only pick up really specific changes (respectively "equalizing" and "facilitation") and nothing else.

>>>>

```{r, echo = FALSE}
## Extracting all the scaled results
scaled_results <- extract.table(all_results, scale.method = "between")
scaled_within <- extract.table(all_results, scale.method = "within")

## Re-ordering results for fancyness
new_order <- c(14, 12, 3, 6,
               15, 11, 2, 8,
               7, 4, 5, 13,
               10, 9, 1)
new_names <- c("TPD[TPD]\nevenness",
               "hypervolume[BAT]\nevenness",
               "dendrogram[BAT]\nevenness",
               "dissimilarity[FD]\nevenness",
               "TPD[TPD]\ndivergence",
               "hypervolume[BAT]\ndispersion",
               "dendrogram[BAT]\ndispersion",
               "dissimilarity[melodic]\nMPD",
               "dissimilarity[melodic]\nRao",
               "dissimilarity[FD]\nRao",
               "dissimilarity[FD]\ndivergence",
               "TPD[TPD]\nalpha",
               "hypervolume[BAT]\nalpha",
               "convex hull[BAT]\nalpha",
               "dendrogram[BAT]\nalpha")
## TODO: add that to fancy plot as options
```

@@

@@

Figure X2: Simulation results: the y axes represent the different metrics tested (sorted by categories). The different columns represent the different stressors. The x-axes represent the metric values centred on the random changes and scaled by the maximum value for each metric between the four stressors. Negative and positive values signify a decrease/increase in the metric score. The dots represent the median metric value, the full line their 50% confidence interval (CI) and the dashed line their 95% CI. The colours are just here to visually separate the metrics rows but the colour gradient within each row corresponds to a removal of respectively 80%, 60%, 40% and 20% of the data (from top to bottom). Grey lines in the background are a fitted linear model on the scaled metric score function of removal amount and the value displayed is the adjusted R^2 from each of these models. Dashed grey lines represent non-significant models (slope or/and intercept). The grey line plots represent (CI + median) represent distribution of metrics scores not clearly different from the random metric scores (paired t-test p value > 0.05).
